%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Theory}
\label{ch:Theory}

To measure the entropy of a system using a mesoscopic circuit, we use the Maxwell relation and resulting integral.

\begin{equation}
	\label{eqn:MR}
	\left( \frac{\partial \mu }{\partial T} \right)_{p,N} = -\left( \frac{\partial S}{\partial N} \right)_{p,T} , \quad
	\Delta S = \int_{\mu_1}^{\mu_2} \frac{dN(\mu)}{dT}\,\, d\mu
\end{equation}


In other words, by measuring the occupation of a quantum dot as a function of the chemical potential, $N(\mu)$, and varying temperature, $T$, we can derive the change in entropy, $\Delta S$ over that change in occupation.

In systems with few degrees of freedom, the relevant discussion of entropy comes in the form of Boltzmann entropy, $S = k_b \ln \Omega$ with $\Omega$ being the number of available microstates~\cite{schroeder}. In Hartman et al.'s experiment, it was shown that the change in entropy as a quantum dot goes from an occupation of $0 \to 1$ electrons was $\Delta S = k_b \ln 2 - k_b \ln 1 = k_b \ln 2$ as the dot went from only having one possible state to having two possible spin states (spin up and spin down). In addition, it was shown that by applying a large magnetic field, Zeeman splitting of the energy levels in the dot eliminated this degeneracy causing $\Delta S = k_b \ln 1 - k_b \ln 1 = 0$.

In practice, to measure the entropy of a small system using a mesoscopic circuit and the integral from Eqn.~\ref{eqn:MR} we have a few requirements. First, we assumed constant pressure in the Maxwell relation. In the context of a 2-dimensional electron gas (2DEG) with which our measurements are conducted, the dominating pressure at temperatures below the Fermi temperature, $T_F \approx 100$K is the degeneracy pressure~\cite{ashcroftmermin}, an incompressibility emerging from the Pauli exclusion principle disallowing fermions from occupying the same quantum state. In addition, by keeping energy fluctuations due to thermal energy, $k_bT$, much smaller than the spacing between energy levels in the dot, we ensure that random temperature fluctuations do not produce unpredictable energy level occupation.
\endinput

Any text after an \endinput is ignored.
You could put scraps here or things in progress.
